---
title: "SlimPosition: *Slim*med down Ex*Position*"
output: html_document
layout: page
---

<!-- 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
-->

```{r options, echo=F, include=F}
library(knitr)
```

# ExPosition

The [ExPosition](https://cran.r-project.org/web/packages/ExPosition/index.html) family of packages are built around one technique: the generalized singular value decomposition (GSVD). 

SlimPosition is a new package in the ExPosition family of packages. As of now, SlimPosition is a successor to the current family of ExPosition packages but in the future, SlimPosition will be *the* core of ExPosition. 


## The Generalized Singular Value Decomposition

Let us call $\mathbf{X}$ a data matrix with $I$ rows and $J$ columns. The singular value decomposition (SVD) of $\mathbf{X}$ is defined as:

$$
\begin{equation}
\mathbf{X} = \mathbf{U \Sigma V}^{\text{T}} \label{eq:svd}
\end{equation}
$$
The SVD gives us three matrices: 

1. the left singular vectors, $\mathbf{U}$, associated with the rows of $\mathbf{X}$
2. the right singular vectors, $\mathbf{V}$, associated with the columns of $\mathbf{X}$
3. the singular values, $\mathbf{\Sigma}$, which explains the variance of $\mathbf{X}$


$\mathbf{\Sigma}, \text{ and } \mathbf{V}$. 





1. $L$ is the rank of ${\bf X}$ where $L \leq J < I$ if ${\bf X}$ is full rank

2. ${\bf \Sigma}$ is the $L \times L$ diagonal matrix of singular values and ${\bf \Lambda}$ is the diagonal matrix of eigenvalues (squared singular values), 

3. ${\bf X}^{T} = ({\bf U\Sigma V}^{T})^{T} = {\bf V\Sigma U}^{T}$,  

4. ${\bf U}$ and ${\bf V}$ are orthonormal left and right singular vectors of sizes $I \times L$ and $J \times L$, respectively where ${\bf U}^{T}{\bf U} = {\bf I} = {\bf V}^{T}{\bf V}$. Furthermore, ${\bf U}^{T} = {\bf U}^{+}$ and ${\bf V}^{T} = {\bf V}^{+}$. Finally, if ${\bf X}$ is full rank ${\bf V}^{T}={\bf V}^{-1}$.


