---
title: "SlimPosition: *Slim*med down Ex*Position*"
output: github_document
---

<!-- 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
-->

```{r options, echo=FALSE}
library(knitr)
opts_chunk$set(fig.path=paste0("figure/", sub("(.*).Rmd","\\1",basename(knitr:::knit_concord$get('infile'))), "-"))
```

# ExPosition

The [ExPosition](https://cran.r-project.org/web/packages/ExPosition/index.html) family of packages are built around one technique: the generalized singular value decomposition (GSVD). 

SlimPosition is a new package in the ExPosition family of packages. As of now, SlimPosition is a successor to the current family of ExPosition packages but in the future, SlimPosition will be *the* core of ExPosition. 


# The Generalized Singular Value Decomposition

Let us call $\mathbf{X}$ a data matrix with $$I$$ rows and $$J$$ columns. The singular value decomposition (SVD) of $${\bf X}$$ is defined as:

\begin{equation}
  {\bf X} = {\bf U \Sigma V}^{T}
\end{equation}


