---
title: "The Generalized Singular Value Decomposition"
output: 
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# GSVD

The generalized singular value decomposition (GSVD) is a [name shared by two different SVD techniques](https://en.wikipedia.org/wiki/Generalized_singular_value_decomposition). This package is for the "weighted" or "vector-constrained" GSVD. For one of the most straight forward introductions to the SVD and GSVD see the Appendices of Greenacre (1984). 

## Background

The GSVD generalizes in two ways: 

1. it generalizes the standard SVD to allow for constraints or weights to be applied to the left and right singular vectors, and

2. it generalizes many multivariate techniques, e.g., principal components analysis (PCA), correspondence analysis (CA), canonical correlation analysis (CCA), partial least squares (PLS), multidimensional scaling (MDS), linear discriminant analysis (LDA), and many many more.

The GSVD is an extraordinarily powerful and flexible tool for multivariate analyses. 


## Package overview

This `GSVD` package is the first and most important package in the family of ExPosition2 packages. The `GSVD` package is a focused package with one goal: give `R` users better and simpler access to the GSVD. `GSVD`'s companion packages will allow users more direct access to specific methods.

`gsvd()` is an efficient pure `R` implementation of the GSVD with no (current) dependencies. However, in the not-so-distant future, we plan to make `GSVD` better, faster, and more efficient with the use of `Rcpp` and `Matrix`. 


## Installation

The `GSVD` package is not yet on CRAN but should be soon. For now, the simplest approach to installation is through the `devtools` package:

```{r, eval = FALSE}
# devtools install via github
devtools::install_github("derekbeaton/ExPosition-Family",subdir="/ExPosition2/GSVD/Package")
```

## Usage

### Core

### Bells-and-whistles

## And beyond!

## References

1. Greenacre, M. (1984). Theory and applications of correspondence analysis. Academic Press.
